Getting the Ball Rolling: Producing a Foundation Text for a Universal Corpus of the World's Languages

### 2014-03-20 docs/computEL/intro.tex
continuing with intro

To produce the HLPSC, we have drawn on four web sources, described in section \ref{sec:sources}. To bring the four resources into a single common format and data structure (section \ref{sec:structure}), each required different degrees and types of cleaning and standardisation. We describe the steps required in detail in section \ref{sec:case_studies}, presenting each resource as a separate case study. By doing so we hope to make future resource conversion efforts more efficient, as they can be guided by the lessons we learned in assembling our seed corpus.

We believe the resulting corpus, which at present covers 1374 languages from 106 language families, is the first of its kind: large enough and consistent enough to allow broadly multilingual language processing. \textcolor{blue}{[START HERE]}

>>>>

To produce the HLPSC, we have drawn on four web sources, described in section \ref{sec:sources}. To bring the four resources into a single common format and data structure (section \ref{sec:structure}), each required different degrees and types of cleaning and standardisation. We describe the steps required in detail in section \ref{sec:case_studies}, presenting each resource as a separate case study. By doing so we hope to make future resource conversion efforts more efficient, as they can be guided by the lessons we learned in assembling our seed corpus. To that end, many of the resources described in \ref{sec:related} are perhaps candidates for inclusion in the next stage of building a UC.

We believe the resulting corpus, which at present covers 1374 languages from 106 language families, is the first of its kind: large enough and consistent enough to allow broadly multilingual language processing. To test this belief, we use the HLPSC in a test application (\ref{sec:cluster}): the task of language clustering. We use surface-level features extracted from our data to estimate the similarity of two languages.
